\begin{abstract}
  %\textcolor{red}{The Modified Interior Penalty (MIP) Diffusion Synthetic Acceleration (DSA) technique
  %is extended to the Piece-Wise Linear Discontinuous (PWLD) finite elements.}
	In this paper, a Diffusion Synthetic Acceleration (DSA) technique applied to the \sn radiation transport equation
	is developed using Piece-Wise Linear Discontinuous (PWLD) finite elements on arbitrary polygonal grids.
%	
  The discretization of the DSA equations employs an Interior Penalty technique, as is classically done for the stabilization of  
  the diffusion equation using discontinuous finite element approximations.
  The penalty method yields a system of linear equations that  
  is Symmetric Positive Definite (SPD). Thus, solution techniques such as Preconditioned 
	Conjugate Gradient (PCG) can be effectively employed. 
	Algebraic MultiGrid (AMG) and Symmetric Gauss-Seidel (SGS) are employed as conjugate gradient preconditioners for the MIP 
	system. AMG is shown to be significantly more efficient than SGS.
%	This results in an efficient DSA preconditioner for arbitrary 
%	polygonal meshes. Such grids (which include triangular and tetrahedral meshes as a subset) can be used to model 
%	complex objects; 	they can also be advantageously employed 
%	with locally refined spatial grids without the need to deal with ``hanging nodes''. 
%
	Fourier analyses are carried out and we show that this scheme is
  always stable and effective at reducing the spectral radius for iterative transport
  solves, even for grids with high-aspect ratio cells.
  Numerical results are presented for different grid types: quadrilateral, hexagonal, and polygonal grids as well as grids
	with local mesh adaptativity. 
%
\end{abstract}
